### 2016-09-26 results.tex
restructuring

\subsection{Classical Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following theorem proves correctness for this construction.  Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.

@@

Turning to privacy, we note immediately that the classical BF, in the ROM, does not meet our SS-privacy notion when the leakage function fails to reveal the entire set~$S$.  This is because the set~$S$ is adversarially chosen, and the adversary has access to the random oracle, i.e. the hash functions used to make~$\pubaux$.  Thus the adversary can simply check that the $\pubaux$ it receives is correct.  Thus, unless $m,k,n$ are such that the false-positive rate is large, the simulator needs to call the random oracle\tsnote{I assume the simulator gets access to the RO?} on the points in~$S$ in order to ``fool'' the adversary.
\tsnote{I'm still not completely comfortable with this.  It isn't explicit in our SS notion, but I assume that~$A$ is stateful and so knows~$S$ in its second stage?  If so, I wonder if the classic BF in the ROM would be secure relative to a weaker notion (but still stronger than OW) in which the second stage does not know~$S$?  This seems likely to me.}

@@

For now, let $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).  The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.

@@

The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\todo{Privacy theorem.  Follows from Jon's general theorem.}
\begin{theorem}\label{thm:lin-privacy}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}. For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

@@

%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
\subsection{Bigram Linear-PRF construction}
%\heading{Bigram Linear-PRF construction (``Neidermayer''). }
\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}

@@

Next we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.  Consider the following leakage function.  On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets x_n[1:|x_n|-1]$ and returns $\mathsf{leak}(S)=\{x_1,x_2,\ldots,x'_n\}$.

@@

\subsection{Domain-separated PRF-Hash}
%\heading{Construction of PRF with domain separation.}
Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
As with the preceding theorem, the following says (informally) that
if~$F$ is a secure PRF, then this domain-separated PRF construction is
correct against adaptive adversaries.  
\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
We note that Neidermayer et
al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
the previous construction with independently keyed PRFs as a way to
thwart their attacks.  The construction we consider now achieves the
same end, albeit via explict domain separation rather than separate
keys.

@@

The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general
result, Theorem~\ref{thm:xxx}.

@@

\subsection{Domain-separated PRF-Hash}
%\heading{Construction of PRF with domain separation.}
Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
As with the preceding theorem, the following says (informally) that
if~$F$ is a secure PRF, then this domain-separated PRF construction is
correct against adaptive adversaries.  
\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
We note that Neidermayer et
al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
the previous construction with independently keyed PRFs as a way to
thwart their attacks.  The construction we consider now achieves the
same end, albeit via explict domain separation rather than separate
keys.

>>>>

\subsection{Classical Bloom filter in random oracle model (ROM). }

\heading{Correctness. }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following theorem proves correctness for this construction.  Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.

@@

\heading{Privacy. }
Turning to privacy, we note immediately that the classical BF, in the ROM, does not meet our SS-privacy notion when the leakage function fails to reveal the entire set~$S$.  This is because the set~$S$ is adversarially chosen, and the adversary has access to the random oracle, i.e. the hash functions used to make~$\pubaux$.  Thus the adversary can simply check that the $\pubaux$ it receives is correct.  Thus, unless $m,k,n$ are such that the false-positive rate is large, the simulator needs to call the random oracle\tsnote{I assume the simulator gets access to the RO?} on the points in~$S$ in order to ``fool'' the adversary.
\tsnote{I'm still not completely comfortable with this.  It isn't explicit in our SS notion, but I assume that~$A$ is stateful and so knows~$S$ in its second stage?  If so, I wonder if the classic BF in the ROM would be secure relative to a weaker notion (but still stronger than OW) in which the second stage does not know~$S$?  This seems likely to me.}

@@

\heading{Correctness. }
For now, let $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).  The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.

@@

\heading{Privacy. }
The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:lin-privacy}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}. For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ such that, for any adversary~$A$
\[
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

@@

%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
\subsection{Bigram Linear-PRF construction}
%\heading{Bigram Linear-PRF construction (``Neidermayer''). }
\heading{Correctness.} 
\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}

@@

\heading{Privacy. }
Next we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.  Consider the following leakage function.  On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets x_n[1:|x_n|-1]$ and returns $\mathsf{leak}(S)=\{x_1,x_2,\ldots,x'_n\}$.

@@

\subsection{Domain-separated PRF-Hash}
%\heading{Construction of PRF with domain separation.}
\heading{Correctness. }
Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
As with the preceding theorem, the following says (informally) that
if~$F$ is a secure PRF, then this domain-separated PRF construction is
correct against adaptive adversaries.  
\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
We note that Neidermayer et
al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
the previous construction with independently keyed PRFs as a way to
thwart their attacks.  The construction we consider now achieves the
same end, albeit via explict domain separation rather than separate
keys.

@@

\heading{Privacy. }
The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general
result, Theorem~\ref{thm:xxx}.

@@

\subsection{Bigram Domain-Separated PRF-Hash}
We note that Neidermayer et al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
the previous construction with independently keyed PRFs as a way to
thwart their attacks.  The construction we consider now achieves the
same end, albeit via explict domain separation rather than separate keys.
\todo{Privacy proof, at a minimum... if it is actually secure.}

\begin{verbatim}
%------------------------------------%
\end{verbatim}
